Accelerating parameter inference with graphics processing units

### 2019-02-08 paper/paper.tex
paper.tex: add more good ideas to conclusion:

>>>>

When suitable surrogate models are available, the overall code performance and thus latency could be yet again further
reduced by eliminating the iteration and fitting stages entirely, performing one Monte Carlo at once
\cite{gwastro-PE-AlternativeArchitecturesROM}.  This approach exploits a linear representation of  $h_{lm}(t)$  via
basis functions, to enable rapid likelihood evaluation as a function of both extrinsic parameters and  $\lambda$.
Though not necessarily or compactly available for all surrogate models, particularly for the small basis sizes necessary
to fit onboard GPUs, this approach could enable exceedingly low latency at small computational cost.  This alternative
architecture would be exceptionally well-suited to the alternative applications of low-latency PE described above.
